---
title: "Creating 96-Well Plates in R"
author: "Lok Raj Joshi"
date: '2018-07-23T21:13:14-05:00'
categories: R
tags:
- R
- Virus neutralization test
---

This week I did some virus neutralization test and I was wondering if there is any way to show the results in 96-well plate format. I was trying to find if there is any R package that can do this. Actually there is one (or might be more). I found a package called **platetools** that can plot values in plate format. 

Let's see how I used this package.



```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

# R Markdown

First load all the required packages

```{r warning=FALSE}
library(ggplot2)
library(platetools)
library(viridis)
```

Prepare your datasets.I prepared in R as shown below. 



```{r}
data=read.csv("df.csv")
data
```

Finally plot your data 
```{r}
plate_id <- rep(c("My Plate"), each = 96)

z_grid(data = data$vals,
       well = data$well,
       plate_id = plate_id) +
  ggtitle("Virus Neutralization Test")
```

Here, the label is not useful for me because I am interested only in positive and negative wells. But it can be useful in plotting ELISA plates. 


